TeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{John Verghese}{September 1, 1994}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:john1.verghese@gmail.com}{john1.verghese\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}2022978344\sbull

\href{http://www.linkedin.com/in/ciesbreijs}{www.linkedin.com/in/ciesbreijs}
\\
Mathenesserplein 84\sbull
3022\thinspace {\large \sc ld}\sbull
Rotterdam\sbull
The Netherlands

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing
before and after




\spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\headedsection
  {\href{http://truetopiaproject.org}{Bank of America-ETT}}
  {\href{http://truetopiaproject.org}{truetopiaproject.org}} {%
  \headedsubsection
    {Initiator}
    {Nov \apo07 -- Apr \apo10}
    {\bodytext{The Truetopia Project is an open source web application (Rails)
to facilitate self-governing communities.  It provides a workflow for
collaborative problem identification and solution design.}}
}


\headedsection
  {\href{http://www.commuun.nl}{Commuun}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Senior Visionary}
    {Jul \apo06 -- Sep \apo09}
    {\bodytext{Set up the technical infrastructure, defined the core competences
and created a brand together with Peter Duijnstee (the proprietor of Commuun).
Then collaborated on several web applications (all Rails apps) within the
context of his company.}}
}

\headedsection
  {\href{http://www.eur.nl}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Guest Lecturer}
    {Jul \apo06 -- Jul \apo09}
    {\bodytext{Conducted a guest lecture on the phenomenon of open source, as
part of the first year curriculum of \emph{Computer Science \& Economics}.}}
}

%\headedsection
%  {LIP Automatisering}
%  {\textsc{Breda, The Netherlands}} {%
%  \headedsubsection
%    {Software Auditor}
%    {Sep \apo06}
%    {\bodytext{Audited their flag ship product \emph{\acr{LIP} Suite}:\ an
%    %\acr{ERP} solution for construction companies.}}
%}

\headedsection
  {\href{http://www.thehealthagency.com}{The Health Agency}}
  {\textsc{Delft \& Rotterdam, The Netherlands}} {%

  \headedsubsection
    {Software Engineer}
    {Jun \apo05 -- Feb \apo06}
    {\bodytext{Worked on their CMS (written in Python and uses Postgre\acr{SQL},
\acr{XML}/\acr{XSLT} and Twisted).}}

  \headedsubsection
    {Software Auditor}
    {Dec \apo06}
    {\bodytext{Assessed their Python/Zope/\acr{Z}o\acr{DB}-based web framework
re-engineering project.}}
}

\vspace{-0.2em}
\begin{center}
  \emph{\small Please refer to my
\href{http://www.linkedin.com/in/ciesbreijs}{Linked-in profile} for a more
complete list of work experiences along with recommendations.}
\end{center}


\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.eur.nl/english}{Erasmus University Rotterdam}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Bachelor degree in Computer Science \& Economics}
    {2004 -- 2007}
    {\bodytext{Focused on the economics of open source, rapid application
development (\acr{RAD}) and the semantic web technology stack
(\acr{RDF}/\acr{RDFS}, \acr{OWL} and \acr{SPARQL}).  Picked up quite some Java
skills along the way.}}
}

\headedsection
  {\href{http://www.tudelft.nl/en}{Technical University Delft}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {Industrial Design Engineering \textnormal{\textit{~(discontinued)}}}
    {2001 -- 2002} {}
}

\headedsection
  {\href{http://www.libanonlyceum.nl}{Libanon Lyceum}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {\acr{VWO} \textnormal{~(pre-university secondary education)}}
    {1994 -- 2000} {}
}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging'
paragraph
  {Technical expertise:}
  {Software design and implementation, with(in) a team.  Big fan of Agile
methodologies (Scrum and Kanban), automated deployment (Capistrano) and
continuous integration (Hudson/Jenkins).  Enjoys writing Ruby/\nsp Python/\nsp
Java/\nsp \CPP, yet flirts regularly with Haskell.  Solid knowledge of web
technologies:\ \acr{HTML+CSS}, \acr{XML}, \acr{RDF}, \acr{REST}, \acr{SOAP} and
JavaScript (mostly Angular and jQuery).  Linux administration skills:\ Bash,
Apache, My\acr{SQL}, Postgres\acr{SQL}, virtualization/cloud (Vagrant,
Open\acr{VZ}, \acr{VM}ware, \acr{KVM}, Xen and \acr{EC}2), datacenter automation
(Puppet and Chef).}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)},
German \emph{(limited working proficiency)}, French \emph{(elementary
proficiency)} and Mandarin Chinese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, Go (board game), history, music, open source,
philosophy, software engineering (methodologies), travel, typography (e.g.\
graphic design, \LaTeX), \acr{UI}/\acr{UX}-design and vegetarian/vegan cooking.}


\end{document}

＀

